Effects of the body force on the evacuation dynamics

### 2020-01-10 paper.tex
agregue mas texto y figuras a la parte de corridor de resultados

The reason why the velocity reduces as the stiffness of the pedestrians increases is that it becomes harder for the pedestrians to walk forward since the repulsion force (body force) against the pedestrian that is ahead becoming higher. Thus, they have no other option than moving at (almost) the same speed than the pedestrians that they have at their sides.\\

\begin{figure}[htbp!]
\centering
\includegraphics[width=0.7\columnwidth]{./kn_vs_vx_corridor.eps}
\caption{\label{kn_vs_vx_corridor}   }
\end{figure}

The value of $k_n$ affects the velocity all along the corridor. Fig... shows the velocity profile ($v_x$ vs. the longitudinal coordinate $y$) for different $k_n$ values. For $k_n=0$, we can see a parabolic-like velocity profile that resembles the Poissele flow for a viscous liquid. As $k_n$ increases the velocity profile flattens until becoming a constant ($k_n=$ 1.2~E6) which $v_x$ value is much lower than on the case of soft pedestrians ($k_n=$0).\\

If the stiffness is high enough, the crowd behaves like a solid; this means that the crowd can not be deformed. This is express by the strain rate, which is shown in Fig.~\ref{}. \\

The strain rate is a quantity that characterizes the deformation of a physical object. It is defined as a tensor .... For this particular problem we define a discrete version of the strain rate that compares the velocity of the pedestrians close to the wall (boundary) and the pedestrians that are in the center of the corridor (center). \\

>>>>

The reason why the velocity reduces as the stiffness of the pedestrians' increases is that it becomes harder for pedestrians to walk forward. The difficulty arises because the pedestrian feels a much higher repulsion from the pedestrian ahead (due to the body force increment). Thus, they have no other option than moving at (almost) the same speed as the pedestrians that they have at their sides. This microscopic mechanism explains the macroscopic behavior of the crowd that turns the crowd from a fluid-like state into a solid-like state. When the stiffness is high enough (say $k_n=$1.2~E6), all the pedestrians walk at the same velocity. The pedestrians that walk in physical contact with the wall are the ones who determine the velocity of the whole crowd.\\

\begin{figure}[htbp!]
\centering
\includegraphics[width=0.7\columnwidth]{./kn_vs_vx_corridor.eps}
\caption{\label{kn_vs_vx_corridor} Mean velocity in the longitudinal coordinate $(v_x)$ as a function of the stiffness $k_n$ for three different global densities (see label in the plot). The measurements correspond to a corridor of 28~m $\times$ 22~m with periodic boundary conditions and $v_d=1$.      }
\end{figure}

The value of $k_n$ affects the velocity all along the corridor. Fig.~\ref{vx_profile} shows the velocity profile ($v_x$ vs. the longitudinal coordinate $y$) for different $k_n$ values. For $k_n=0$, we can see a parabolic-like velocity profile that resembles the Poiseuille flow (for Newtonian and incompressible fluids in laminar flow flowing through a pipe). As $k_n$ increases the velocity profile flattens until becoming a constant ($k_n=$ 1.2~E6) which $v_x$ value is much lower than on the case of soft pedestrians ($k_n=$0).\\

If the stiffness is high enough, the crowd behaves like a solid; this means that the crowd can not be easily deformed. In this context, to deform means to have parts of the crowd that move faster than other parts of the crowd. \\

The strain rate is a tensor for every point in the space. It expresses how the relative velocity of a medium changes when one moves away from a position in a specific direction. For this particular problem, we define the following version of the strain rate:

\begin{equation}
S = \frac{<v_x(center)> - <v_x(boundary)> }{\left | y(center) - y(boundary) \right |} 
\end{equation}

Where $<>$ means the average taken over time. By this definition we compare the velocity of the pedestrians close to the wall (boundary) with respect to the velocity of the pedestrians in the center of the corridor (center). As the stiffness level increases, the crowd becomes less deformable. This phenomenon is shown in Fig.~\ref{strain_rate_vs_kn} where we can see that the strain rate decreases with $k_n$. \\

\begin{figure}[!htbp]
\centering
    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./vx_profile.eps}\label{vx_profile}}\ 
    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./strain_rate_vs_kn.eps}\label{strain_rate_vs_kn}}\\
\caption[width=0.47\columnwidth]{(a) Velocity in the $x$ coordinate as a function of the transversal coordinate $y$ for three different stiffness values $k$ (see the label). (b) Strain rate as a function of the stiffness level $k$.  The measurements correspond to a corridor of 28~m $\times$ 22~m with periodic boundary conditions and $v_d=1$. The global density was 7 p~m$^{-2}$.  }
\label{profile_strain}
\end{figure}

To conclude this section, we remark that increasing the stiffness produces the opposite results in corridors respect to bottlenecks. The walls in the corridors play a critical role that prevents pedestrians from detaching from each other. This effect has consequences such as increasing the connectivity of the contact network, flattening the velocity profile (thus reducing the strain rate). If the stiffness is high enough, the pedestrians can not push to the pedestrian ahead since the body force repulsion becomes very high. This leads to a"solidification" of the crowd that makes all the pedestrians walk at almost the same velocity. The pedestrians that are in contact with the wall are the ones who determine the velocity of the whole crowd. \\
